# Data transformation

Since the data from these three decades contains different number and names of columns, we need to standardize the dataset column for further analysis.

## Load datasets
```{r}
#load raw datasets
census1995<-read.csv("1995_Street_Tree_Census.csv")
census2005<-read.csv("2005_Street_Tree_Census.csv")
census2015<-read.csv("2015_Street_Tree_Census_-_Tree_Data.csv")
```

Print column names of census 1995
```{r}
colnames(census1995)
```

Print column names of census 2005
```{r}
colnames(census2005)
```

Print column names of census 2015
```{r}
colnames(census2015)
```

## Data Transformation
In our analysis, we will not use all of the information listed in the datasets. So, we need to filter out useful columns for our analysis.

For our analysis, we need the following variables: the ID of the tree, the name of tree's species, the postcode of tree's location, the borough of tree's location and the diameter of stump.

Show part of the tree census 1995 after selection:
```{r}
library(dplyr)
#census 1995 transformation
census1995_1<-census1995%>%
  select(RecordId,Spc_Latin,Postcode_Original,Borough,Diameter)%>%
  rename(ID = RecordId,Species = Spc_Latin,Postcode = Postcode_Original)%>%
  mutate(Year = 1995)
head(census1995_1)
```

Show part of the tree census 2005 after selection:
```{r}
#census 2005 transformation
census2005_1<-census2005%>%
  select(OBJECTID,spc_latin,zipcode,boroname,tree_dbh)%>%
  rename(ID = OBJECTID, Species = spc_latin,Postcode = zipcode,Borough = boroname,Diameter=tree_dbh)%>%
  mutate(Year = 2005)
head(census2005_1)
```

Show part of the tree census 2015 after selection:
```{r}
#census 2015 transformation
census2015_1<-census2015%>%
  select(tree_id,spc_latin,postcode,borough,tree_dbh)%>%
  rename(ID = tree_id,Species = spc_latin,Postcode = postcode,Borough = borough,Diameter = tree_dbh)%>%
  mutate(Year = 2015)
head(census2015_1)
```

```{r}
#combine these three dataset
data<-rbind(census1995_1,census2005_1,census2015_1)
```